%------------------------------------------------------------------------------%
% PERSONAL INFO
%------------------------------------------------------------------------------%

\name{Hanafe Mira}
\tagline{Software Engineer (Java, Mobile, Security, DevOps, IoT)}

\personalinfo{
  \email{miraahanafee@gmail.com}
  \phone{+94 76 381 1834}
  \location{Colombo, Sri Lanka}
  \linkedin{hanafe-mira-822096237}
  \github{self1am}
  \homepage{self1am.github.io/HanafeMira}
  \npm{\href{https://www.npmjs.com/~hanafe}{hanafe}}
}

\begin{document}
\makecvheader

%------------------------------------------------------------------------------%
% SUMMARY
%------------------------------------------------------------------------------%
\cvsection{Summary}

\begin{quote}
Results-driven Software Engineer with strong experience in \textbf{Java}, \textbf{React Native}, \textbf{Flutter}, \textbf{Next.js}, and secure backend development. Proven ability in building high-reliability systems including \textbf{wallet applications}, \textbf{KYC pipelines}, \textbf{security validation modules}, and \textbf{loan recovery systems}.  
Architect of multiple \textbf{private scoped GitHub and NPM packages} used internally across engineering teams for validation, shared utilities, and automation.  
Hands-on exposure to IoT through university coursework in \textbf{Cognitive Robotics} and \textbf{Information Systems Security}. Passionate about scalable architectures, distributed systems, and impactful engineering.
\end{quote}

%------------------------------------------------------------------------------%
% EXPERIENCE
%------------------------------------------------------------------------------%
\cvsection{Experience}

\cvevent{Software Engineer (Associate Level Responsibilities)}{JF Connect (Private) Ltd}{May 2025 -- Present}{Colombo, Sri Lanka}

\begin{itemize}
  \item Lead developer for several internal and client-facing modules including \textbf{wallet systems}, \textbf{KYC onboarding flows}, and secure \textbf{financial transaction pipelines}.
  \item Implemented key components in Java-based backend services, including authentication, authorization, and high-throughput event-driven features.
  \item Designed and architected a \textbf{Flutter Loan Recovery Module} from scratch; adopted as the internal standard for mobile architecture for its scalability, clean layering, and maintainability.
  \item Built multiple \textbf{private GitHub/NPM packages} to centralize shared logic (validators, utilities, security middleware), improving cross-project consistency and reducing code duplication.
  \item Worked on Hospitality Management Applications, internal dashboards, and cross-functional engineering tasks in mobile, web, and backend.
\end{itemize}

\divider

\cvevent{Software Engineer Intern}{JF Connect (Private) Ltd}{Nov 2024 -- May 2025}{Colombo, Sri Lanka}

\begin{itemize}
  \item Contributed to platform-wide engineering across React Native, Java, Firebase, and secure backend components.
  \item Worked on production-level features in wallet management, user verification, and system integrations.
  \item Developed internal tooling and improved the team’s development pipeline using modules that were later converted into private shared packages.
\end{itemize}

%------------------------------------------------------------------------------%
% EDUCATION
%------------------------------------------------------------------------------%
\cvsection{Education}

\cvevent{BSc. (Hons) in Information Systems}{University of Colombo School of Computing}{Expected Graduation: 2025}{Colombo, Sri Lanka}

Relevant Coursework: Distributed Systems, Software Engineering, Data Structures \& Algorithms, Information Security, Cognitive Robotics, Mobile Application Development, Enterprise Applications.

Research Interests: Quantum Machine Learning, Relativistic Physics, Blockchain Systems, Machine Learning in Security.

%------------------------------------------------------------------------------%
% PROJECTS
%------------------------------------------------------------------------------%
\cvsection{Key Projects}

\cvevent{Private Scoped GitHub / NPM Packages}{}{Ongoing}{}
\begin{itemize}
  \item Published and maintained multiple private scoped packages for internal use, including:
  \begin{itemize}
    \item Centralized NIC and Passport validation library  
    \item React Native utility and component modules  
    \item Node.js/Next.js shared middleware packages  
  \end{itemize}
  \item Improved team productivity through unified validation and shared tooling.
\end{itemize}

\cvevent{Loan Recovery Mobile Module (Flutter)}{}{}{}
\begin{itemize}
  \item Architected a full-scale enterprise module from the ground up.
  \item Adopted company-wide for its clean architecture, domain-driven approach, and maintainability.
\end{itemize}

\cvevent{Self-Driven Car Simulation (ML)}{}{}{}
\begin{itemize}
  \item Built a machine-learning-driven autonomous car model in JavaScript.
  \item Designed neural networks for steering, speed prediction, and real-time traffic navigation.
\end{itemize}

\cvevent{WellnessVision (React + Tailwind + Firebase)}{}{}{}
\begin{itemize}
  \item Frontend developer for a full digital health platform connecting medical professionals and patients.
\end{itemize}

%------------------------------------------------------------------------------%
% SKILLS
%------------------------------------------------------------------------------%
\cvsection{Skills}

\cvtag{Java}
\cvtag{Spring Boot}
\cvtag{REST APIs}
\cvtag{SQL / PostgreSQL}
\cvtag{Node.js}
\cvtag{Next.js}
\cvtag{React Native}
\cvtag{Flutter}
\cvtag{TypeScript}
\cvtag{Docker}
\cvtag{CI/CD}
\cvtag{Software Architecture}
\cvtag{GitHub Actions}
\cvtag{IoT (Fundamentals)}
\cvtag{Security \& KYC Systems}

%------------------------------------------------------------------------------%
% IoT & SECURITY EXPERIENCE
%------------------------------------------------------------------------------%
\cvsection{IoT \& Security Experience}

\begin{itemize}
  \item Built a CLI tool for scanning open ports on IoT devices based on IP range (Information Systems Security coursework).
  \item Hands-on use of sensors and microcontrollers during Cognitive Robotics coursework.
  \item Applied security-layer thinking in wallet systems, authentication stacks, and financial products.
\end{itemize}

%------------------------------------------------------------------------------%
% REFERENCES
%------------------------------------------------------------------------------%
\cvsection{References}
Available upon request.

\end{document}
